AhirV2: Tools which take algorithms to hardware \\ A reference manual

### 2020-10-28 Documents/AhirV2/AhirV2ToolsReference.tex
Fixed butt stupid bug in register_file_1w_1r_port.vhd. Also some issues related to constant phi statements. Updated docs a bit.

The flow of transformations is illustrated in Figure \ref{fig:AhirFlow}.
\begin{figure}
\begin{centering}
\centerline{\psfig{figure=AHIRv2Flow.eps,width=3.0in,height=3.0in}}
\caption{AhirV2 flow}
\end{centering}
 \label{fig:AhirFlow}
\end{figure}

@@

>>>>

The flow of transformations is illustrated in Figure \ref{fig:AhirFlow}.
\begin{figure}
\centering
\includegraphics[width=8cm]{AHIRv2Flow.pdf}
\caption{AhirV2 flow}
 \label{fig:AhirFlow}
\end{figure}

@@

\subsection{{\bf AaPreprocess}: Preprocessor for {\bf Aa} description}

The {\bf AaPreprocess} utility takes an input \Aa file and applies pre-processing
directives in the file  to produce an output \Aa file.   The invocation of the
{\bf AaPreprocess} utility is as follows:
\begin{verbatim}
AaPreprocess [-I <search-directory>]* -o <output-aa-file> <list-of-input-aa-files>
\end{verbatim}

The utility then applies the pre-processing directives in the input \Aa files
to produce an output \Aa file.

The pre-process directives that are supported are
\begin{description}
\item[\#include]  Specify a file to be included.  This is typically specified
as 
\begin{verbatim}
#include foo.aa
\end{verbatim}
The directories specified by the -I option are searched and the first
matching file with name ``foo.aa'' is substituted in place at the point
of the include.
\item[\#define]  Specifies a key-word definition.  For example
\begin{verbatim}
#define P  const_56
\end{verbatim}
This defines the  string "P" to be an alias of the string "const\_56".
A \#define can override another \#define.  The last definition is used.
\item[\#undefine]  This removes the specified define from the list
of preprocessor defines.
\begin{verbatim}
#undefine P
\end{verbatim}
Any further references to ``P'' in the source will be
flagged as errors by the pre-preocessor.
\item[\#\#]  This the paste directive.   For example, if we have
defined
\begin{verbatim}
#define P  const_56
\end{verbatim}
and we have a line in the input file of the form
\begin{verbatim}
a := ( ##P + 1)
\end{verbatim}
then, this will be expanded to
\begin{verbatim}
a := (const_56 + 1)
\end{verbatim}
\item [\#if - \#endif] 
Code can be conditionally included using this construct.
\begin{verbatim}
#define TFLAG 1
#define SFLAG 0
#if TFLAG
a := b
#endif 
#if SFLAG
b := a
#endif
\end{verbatim}
will be expanded to
\begin{verbatim}
a := b
\end{verbatim}
\end{description}

To summarize: the preprocessor can be used to 
\begin{itemize}
\item include a file into the code.
\item paste strings into the code.
\item conditionally include code.
\end{itemize}
This adds flexibility to the programmer and
can reduce the amount of repetitive code.
